Supplemental Materials for: Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-04-14 doc/peakcharacterization_supplemental.Rmd
and rsd plots to supplemental

@@

`r figure_count$label_text("p_value")`.
**A**: Log-p-values generated by comparing non-cancer and cancer sample IMFs using peak intensities from raw and corrected peak intensities, where the corrected intensities were normalized using the sample raw median intensities.
Red line denotes perfect agreement.
**D**: Sina plot of differences in the log-p-values generated by corrected intensity normalized by the raw median intensities.
Also shown are the Bonferroni adjusted p-values from a t-test of the log-p-value differences for each method.
Green points denote the high, mean, and low-confidence limits reported from the t-test.

>>>>

## RSD of Methods for Higher Intensity Peaks

```{r increment_rsd_method}
figure_count$increment("rsd_method")
table_count$increment("rsd_method")
```

`r figure_count$label_text("rsd_method")` and `r table_count$label_text("rsd_method")` we plot and summarize the RSD distributions by sample and method for those peaks with a Log10(mean) intensity ≥ 5.
The distributions are shifted to the left compared to using all peaks, but the overall patterns are the same.

```{r rsd_method, dn_id = figure_count}
tar_load(rsd_plot_int)
wrap_plots(rsd_plot_int, ncol = 2)
```

`r figure_count$label_text("rsd_method")`.
Density plots of relative standard deviations (RSD) of peak heights across scans for each of the processing methods.
A peak had to have a Log10(mean) intensity ≥ 5 for the RSD value to be reported.

`r table_count$label_text("rsd_method")`.
RSD means, medians, modes, and maximum observed values for each sample with different overall processing.
Only peaks with a Log10(mean) intensity ≥ 5 are included.

```{r rsd_method_table}
tar_load(rsd_best_int)
rsd_best_int %>%
  autofit()
```

## Peak Variance

```{r increment_peak_variance}
tar_load(rsd_combine)
figure_count$increment("peak_variance")
```

```{r peak_variance, dn_id = figure_count, fig.width = 8, fig.height=9}
filtersd_only = rsd_combine %>%
  dplyr::filter(processed %in% "filtersd", n_perc >= 0.9)

filtersd_by_sample = split(filtersd_only, filtersd_only$sample)

sd_by_sample = purrr::map(filtersd_by_sample, function(in_sample){
  mean_sd = in_sample %>%
    ggplot(aes(x = log10(mean), y = sd)) +
    geom_point(alpha = 0.5) +
    labs(subtitle = in_sample$sample[1])
  mean_rsd = in_sample %>%
    ggplot(aes(x = log10(mean), y = rsd)) +
    geom_point(alpha = 0.5)
  mean_sd | mean_rsd
})

wrap_plots(sd_by_sample, ncol = 1)
```

`r figure_count$label_text("peak_variance")`.
Standard deviation (SD) and relative standard deviation (RSD) as a function of Log10(mean) intensity for peaks present in ≥ 90% of scans for each sample.

@@

`r figure_count$label_text("p_value")`.
**A**: Log-p-values generated by comparing non-cancer and cancer sample IMFs using peak intensities from raw and corrected peak intensities, where the corrected intensities were normalized using the sample raw median intensities.
Red line denotes perfect agreement.
**B**: Sina plot of differences in the log-p-values generated by corrected intensity normalized by the raw median intensities.
Also shown are the Bonferroni adjusted p-values from a t-test of the log-p-value differences for each method.
Green points denote the high, mean, and low-confidence limits reported from the t-test.

```{r save_counts}
saveRDS(figure_count, file = "doc/supplemental_figure_count.rds")
saveRDS(table_count, file = "doc/supplemental_table_count.rds")
```
